Automatically generated NE tagged corpora for English and Hungarian

### 2012-04-27 paper/engNERwiki.tex
A few words added and others removed.

Discovered entities are tagged with the CoNLL label assigned to them in the entity list extracted from DBpedia. If the link target is not in the entity list, or the link points to a disambiguation page, we can not determine the type of the entity, and tag it as UNK. Links to redirect pages are resolved to point instead to the redirect target, after which they are handled as regular cross-references. Finally, sentences with UNK links in them are removed from the corpus.

@@

To account for such mentions, we apply Nothman's \shortcite{Nothman:08} solution. For each page, we maintain a list of entities discovered in the page so far and try to associate capitalized words in the article text with these entities. We augment the list with the aliases of every entity, such as titles of redirect pages that target it, the first and last names of a \texttt{PER} entity and any numbers in the name. If the current page is a named entity, the title and its aliases are added to the list as well; moreover, as Wikipedia usually includes the original name of foreign entities in the article text, localized versions of the title are also added to the list as aliases.

@@

As mentioned above, sentences with words tagged as \texttt{UNK} are discarded. Furthermore, there are many incomplete sentences in the Wikipedia text: image captions, enumerations items, contents of table cells, etc. On the one hand, these sentence fragments may prove to be of too low quality to be of any use in the traditional NER task. On the other hand, they could prove to be invaluable when training a NER tagger for User Generated Content, which is known to be noisy and fragmented. As a compromise solution, we included these fragments in the corpus, but labelled them as "low quality", so that users of the corpus can decide whether they want to use them or not. A sentence is labelled as such if it either lacks a punctuation mark at the end, or it contains no finite verbs.

>>>>

Discovered entities are tagged with the CoNLL label assigned to them in the entity list extracted from DBpedia. If the link target is not in the entity list, or the link points to a disambiguation page, we cannot determine the type of the entity, and tag it as UNK. Links to redirect pages are resolved to point instead to the redirect target, after which they are handled as regular cross-references. Finally, sentences with UNK links in them are removed from the corpus.

@@

To account for such mentions, we apply Nothman's \shortcite{Nothman:08} solution. For each page, we maintain a list of entities discovered in the page so far and try to associate capitalized words in the article text with these entities. We augment the list with the aliases of every entity, such as titles of redirect pages that target it, the first and last names in case of a \texttt{PER} entity and any numbers in the name. If the current page is a named entity, the title and its aliases are added to the list as well; moreover, as Wikipedia usually includes the original name of foreign entities in the article text, localized versions of the title are also added to the list as aliases.

@@

As mentioned above, sentences with words tagged as \texttt{UNK} are discarded. Furthermore, there are many incomplete sentences in the Wikipedia text: image captions, enumerations items, contents of table cells, etc. On the one hand, these sentence fragments may be of too low quality to be of any use in the traditional NER task. On the other hand, they could prove to be invaluable when training a NER tagger for User Generated Content, which is known to be noisy and fragmented. As a compromise solution, we included these fragments in the corpus, but labelled them as "low quality", so that users of the corpus can decide whether they want to use them or not. A sentence is labelled as such if it either lacks a punctuation mark at the end, or it contains no finite verbs.
